SKIN LESION CLASSIFICATION ON IMBALANCED DATA USING DEEP LEARNING WITH SOFT ATTENTION

### 2022-08-20 MDPI/Sensor Paper/template.tex
Update Paper Ver 12

% Keywords
\keyword{Skin Lesions, Classification, Deep Learning, Soft-Attention, Imbalance)}

@@

\subsubsection{Loss Function}
The loss function used in this paper is categorical cross-entropy. Consider $X = [x_1, x_2, \dots, x_n]$ as the input feature, $\theta = [\theta_1, \theta_2, \dots, \theta_n]$. Let $N$, and $C$ is the number of training examples and number of class respectively. The categorical cross-entropy loss is presented as:
\[L(\theta, x_n) = -\frac{1}{N}\sum_{c=1}^{C}\sum_{n=1}^{N}W_c\times y^c_n \times \log(\hat{y}^c_n)\]
where $\hat{y}^c_i$  is the output of model and $y^c_i$ is the target that the model should return, $W_c$ is the weight of class $c$. Since the data set face the imbalanced problem then class weight for the loss is applied. This formula below is used to calculate the class weight:
\[W = N \odot D\]
\[D = \begin{bmatrix}
	\frac{1}{C \times  N_1} & \frac{1}{C \times  N_2} & \dots & \frac{1}{C \times  N_n}\\
\end{bmatrix} = \frac{1}{C} \odot \begin{bmatrix}
	\frac{1}{N_1} & \frac{1}{N_2} & \dots & \frac{1}{N_n}\\
\end{bmatrix}\]
where $N$ is the number of training sample, $C$ is the number of class, $N_i$ is the number of sample in each class $i$. $D$ is the matrix contain the inverse of $C \times N_i$.

@@

>>>>

% Keywords
\keyword{Skin Lesions, Classification, Deep Learning, Soft-Attention, Imbalance}

@@

\subsubsection{Loss Function}
The loss function used in this paper is categorical cross-entropy. Consider $X = [x_1, x_2, \dots, x_n]$ as the input feature, $\theta = [\theta_1, \theta_2, \dots, \theta_n]$. Let $N$, and $C$ is the number of training examples and number of class respectively. The categorical cross-entropy loss is presented as:
\[L(\theta, x_n) = -\frac{1}{N}\sum_{c=1}^{C}\sum_{n=1}^{N}W_c\times y^c_n \times \log(\hat{y}^c_n)\]
where $\hat{y}^c_i$  is the output of model and $y^c_i$ is the target that the model should return, $W_c$ is the weight of class $c$. Since the data set face the imbalanced problem then class weight for the loss is applied. In this research, both of the original weight and a new weight formula is implementation. Originally, the weight is calculated by taking the inverse of percentage that each class accounts for. The new weight formula is described as follow:
\[W = N \odot D\]
\[D = \begin{bmatrix}
	\frac{1}{C \times  N_1} & \frac{1}{C \times  N_2} & \dots & \frac{1}{C \times  N_n}\\
\end{bmatrix} = \frac{1}{C} \odot \begin{bmatrix}
	\frac{1}{N_1} & \frac{1}{N_2} & \dots & \frac{1}{N_n}\\
\end{bmatrix}\]
where $N$ is the number of training sample, $C$ is the number of class, $N_i$ is the number of sample in each class $i$. $D$ is the matrix contain the inverse of $C \times N_i$.

@@

Besides the comparison between original weight loss based model and the new weight loss based model is also conducted on the three best performance model including InceptionResNetV2, DenseNet201, MobileNetV3. After the experiment, it is found out that the new weight loss function dose not only contribute to the model to overcome the data imbalance problem but it also make the accuracy increase. The performance of models is described in the Table \ref{table:loss-comparision}

\begin{table}[H]
	\centering
	\begin{tabular}{| l | c | c |}
		\hline
		Model & Original Loss Accuracy & New Loss Accuracy\\
		\hline
		InceptionResNetV2 & 0.74 & 0.90\\
		DenseNet201 & 0.81 & 0.89\\
		MobileNetV3 & 0.80 & 0.86\\
		\hline
	\end{tabular}
	\caption{Loss based model accuracy comparison}
	\label{table:loss-comparision}
\end{table}
